---
title: 'Pakcage: Benford.Analysis'
author: "David Jackson"
date: "11/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(scales)
library(dplyr)
library(benford.analysis)
```

### Author: Carlos Cinelli <carloscinelli@hotmail.com>
#### Generates benford object

```{r}
data(corporate.payment) #gets data
cp <- benford(corporate.payment$Amount, 2, sign="both") 
cp #prints 
plot(cp) #plots
```

#### Prints the digits by decreasing order of discrepancies

```{r}
head(suspectsTable(cp),10) 
```

#### Gets observations of the 2 most suspicious groups

```{r}
suspects <- getSuspects(cp, corporate.payment, how.many=2) 
```

#### Prints the duplicates by decreasing order

```{r}
head(duplicatesTable(cp))
```

#### Gets the observations of the 2 values with most duplicates

```{r}
duplicates <- getDuplicates(cp, corporate.payment,how.many=2)
head(duplicates)
```

#### Gets the Mean Absolute Deviation

```{r}
MAD(cp)
```


#### Gets the Chi-squared test


```{r}
chisq(cp)
```

#### Gets observations starting with 50 or 99 

```{r}
digits_50_and_99 <- getDigits(cp, corporate.payment, digits=c(50, 99))
head(digits_50_and_99)
```
```{r}
data(taxable.incomes.1978)
FirstDigit <- substr(taxable.incomes.1978$taxIncomes,1,1)
FD <- as.data.frame(FirstDigit)
CountIncome <- FD %>% group_by(FirstDigit) %>%
  summarize (count=n())
```
```{r}
ggplot(CountIncome) + geom_col(aes(x=FirstDigit,y=count))
```
#### First Two Digits

```{r}
secondDigit <- substr(taxable.incomes.1978$taxIncomes,1,2)
FD1 <- as.data.frame(secondDigit)
```

```{r}
secondIncome <- FD1 %>% group_by(secondDigit) %>%
  summarize (count=n())
```
```{r}
ggplot(secondIncome) + geom_col(aes(x=secondDigit,y=count))
```




