---
title: "Package Bendford Tests"
author: "David Jackson"
date: "11/16/2020"
output: 
  html_document: 
    fig_width: 9
    fig_height: 7
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(scales)
library(BenfordTests)
library(benford.analysis)
library(RSQLite)
```

### Set the random seed to an arbitrary number
* https://youtu.be/7uhAn19V1EY


```{r}
set.seed(421)
```

### Create a sample satisfying Benford's law

```{r}
X<-rbenf(n=50)
X
```

### Look at the first digits of the sample

```{r}
signifd(X)
```

### Perform a Chi-squared Test on the sample's first digits using defaults
```{r}
chisq.benftest(X)
```

### Plot histogram of first digit

```{r}
signifd.analysis(X)
```

### New York Times US COVID-19 Cases and Deaths


```{r}
df <- read.csv("../DATA/us.csv")
df$date <- as.Date(df$date)
Y <- diff(df$cases,lag=1)
Y <- subset(Y, Y >=0)
Z <- diff(df$deaths,lag=1)
Z <- subset(Y,Y>0)
```
```{r}
ggplot(df) + geom_line(aes(x=date,y=cases))
ggplot(df) + geom_line(aes(x=date,y=deaths))
```

#### first digits Cases

```{r}
YY <- signifd(Y)
YY <- subset(YY,YY >=0)
signifd.analysis(YY)

```

### first Digit and Second Deaths

```{r}
X <-signifd(X)
cp <- benford(X, 1, sign="both") #generates benford object
plot(cp) #plots
```
#### US COVID-19 Deaths (From States Data)

```{r}
db <- db <- dbConnect(RSQLite::SQLite(),dbname= "../COVIDDB/COVID.sqlite3")
df <- dbGetQuery(db,"select state,new_cases,new_deaths from COUNTYDAILY ")
X <- df$new_deaths
Y <- df$new_cases
```
```{r}
cp <- benford(X, 1, sign="both") #generates benford object
plot(cp) #plots
```
## First two Digits

```{r}
cp <- benford(X, 2,sign="both") #generates benford object
plot(cp) #plots
```

```{r}
cp <- benford(Y, 1, sign="both") #generates benford object
plot(cp) #plots
```

## Cases first two digits 

```{r}
cp <- benford(Y, 2, sign="both") #generates benford object
plot(cp) #plots
```
#### New York State of Mind

```{r}
NY <- subset(df,state=="New York"  )
XX <- NY$new_deaths
YY <- NY$new_cases
```
```{r}
cp <- benford(XX,1 , sign="both") #generates benford object
plot(cp) #plots
```
```{r}
cp1 <- benford(XX,2 , sign="both") #generates benford object
plot(cp) #plots
```


