---
title: "Dr.  Mark Nigrini;  Benford's Law"
author: "David Jackson"
date: "11/20/2020"
output: 
  html_document: 
    fig_width: 9
    fig_height: 7
---

```{r setup, include=FALSE,error=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(benford.analysis)
library(BenfordTests)
options(scipen=999) 
```

### Benford's Law, Part 3 (Analysis in R, no packages), updated code June 2020
* YouTube: https://youtu.be/F9XjUx47xVY

#### Read in Census Data

```{r}
rm(list=ls())
People <- read.csv("./1_CensusData_2010a.csv")
class(People$People2010)
class(People$Area)
People$People2010 <- as.numeric(People$People2010)
head(People,n=10)
colnames(People)
```

#### People Counts: Min,Max and Mean

```{r}
TotPeople <- format(sum(People$People2010), nsmall=2, big.mark=",")
MinPeople <- format(min(People$People2010), nsmall=2, big.mark=",")
MaxPeople <- format(as.numeric(max(People$People2010)),nsmall=2,scientific=FALSE,big.mark=",")

str(People)
summary(People$People2010)
People<-People[!(People$People2010<0.01),] # Delete records < 0.01

```

#### Multiply records 0.01<=x<10 by 1000 to move decimal point to the right

```{r}
People$People2010 <- ifelse(People$People2010 <10 & People$People2010 >=0.01,
   People$People2010*1000,People$People2010)
```

#### Extract and Sum the Digit Frequencies

```{r}
FT       <- substr(People$People2010,1,2)
FTD      <- as.numeric(FT)
Count    <- aggregate(data.frame(Count=FTD),list(FirstTwo=FTD),length)
FTDCount <- data.frame(Count$FirstTwo, Count$Count)

```

####  Rename the FirstTwo and Count fields

```{r}
colnames(FTDCount)[colnames(FTDCount)=="Count.FirstTwo"]<-"FirstTwo"
colnames(FTDCount)[colnames(FTDCount)=="Count.Count"]<-"Count"
```

#### Check: Is there a positive (>0) count for each possible First-Two Digits?

```{r}
CheckErr1 <- NROW(FTDCount)
CheckErr2 <- sum(FTDCount$FirstTwo)
if(CheckErr1!= 90)   warning('Count of First-Two Digits ne 90')
if(CheckErr2!= 4905) warning('First-Two Digits not = 10:99')
```

#### Prepare the components of the Benford Table

```{r}
FTDigit    <- c(10:99)
Count      <- c(FTDCount$Count)
TotObs     <- sum(Count)
Actual     <- round(Count/TotObs, digits=6)
Benford    <- round(log10(1+1/FTDigit), digits=6)
Difference <- round(Actual-Benford, digits=6)
AbsDiff    <- round(abs(Difference), digits=6)
Zstat      <- round((abs(Actual-Benford)-(1/(2*TotObs)))/(sqrt(Benford*(1-Benford)/TotObs)), digits=6)
Zstat      <- ifelse(Zstat<0, 0, Zstat)
```

#### Combine the components of the Benford Table with reasonableness tests

```{r}
BenTest <- cbind(FTDigit,Count,Actual,Benford,Difference,AbsDiff,Zstat)
head(BenTest, n=5)
tail(BenTest, n=5)
str(BenTest)
summary(Count)

```

####  Calculate the Mean Absolute Deviation (MAD) to assess conformity

```{r}
MAD <- round(mean(AbsDiff), digits = 5)
if(MAD>0.0022){
     con<-"Nonconformity"
}else if(MAD>0.0018) {
     con<-"Marginally acceptable conformity"
}else if(MAD>0.0012) {
     con<-"Acceptable conformity"
}else{
     con<-"Close conformity"
}
#
cat('Our conclusion is:',con,"\n")
write.csv(BenTest, file="BenTest.csv")    # Write the results to a csv file
```

#### Plots of Benford's Law

```{r}
benford <- as.data.frame(BenTest)
attach(benford)
plot(benford$FTDigit,benford$Count,type="h",main="Benford Counts First Two Digits")
plot(benford$Actual,type="h",main="Benford Actual   Percents")
lines(benford$Benford,type="l",col="red",)
```

### R Package: Benford Analysis

```{r}

set.seed(421)
cp <- benford(People$new_deaths, 2, sign="both") 
cp #prints 
plot(cp) #plots

cp1 <- benford(People$new_deaths, 1, sign="both") 
cp #prints 
plot(cp1) #plots
```

### R Package BenfordTests

```{r}

set.seed(421)
X <-signifd(People$new_deaths)
signifd.analysis(X)
```



